\bf Service Chain Placement in SDNs \thanks{ A preliminary version appeared in the 3rd International Workshop on Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017. Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2019-05-24 src/chain.tex
fix model
final DAM

Foerster, Parham and Schmid~\cite{FPS17} considered the
\textsc{Bidirectional Waypoint Routing} problem, where the input
consists of a graph $G = (V,E)$ with edge weights and capacities, a
source $s$, a destination $t$, and a subset of the vertices $W$.  A
feasible solution is a route from $s$ to $t$ that visits the vertices
in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
according to the given order.  The goal is to find a minimum weight
solution.
%
Foerster et al.~\cite{FPS17} showed that the unordered
problem has no PTAS, assuming P$\neq$NP and gave a
$1.53$-approximation algorithm.  They also presented polynomial time
algorithms for special cases.
%
As for the ordered variant, they showed that feasible routes can be
computed efficiently if $\abs{W} = O(1)$.  In addition, they showed
that the problem is NP-hard and gave a polynomial time algorithm for
cactus graphs with constant link capacities.
%
Amiri et al.~\cite{AFS18} considered the unordered case, and they
presneted a polynomial-time algorithm for graphs of bounded treewidth.
%
Amiri et al.~\cite{AFJPS18} studied the ordered case, and they
gave algorithms for special networks.
%
An overview of waypoint routing is given in ~\cite{AFJS18}.

@@

\item[Virtual specification:]
%
  The description of a request for a service chain consists of a
  physical source $s \in V$, a physical destination $t \in V$, and a
  directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
%
%   Without loss of generality, we assume that $p(s) = p(t) = 0$.  
%
  The DAG $\calG$ has a source node $\sigma \in \calV$ and a
  destination $\tau \in \calV$. Each node $\alpha \in \calV$ represent
  a VNF that has a processing demand $p(\alpha)$.
%
  Without loss of generality, we assume that $p(\sigma) = p(\tau) =
  0$.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.

@@

Formally, given a physical network, a virtual specification, and a
parameter $r \in \naturals$, an \emph{$r$-robust} placement is a
collection of $r$ placements, $f_1,\ldots,f_r$, that correspond to $r$
internal vertex disjoint physical paths.%
\footnote{Two paths are internal vertex disjoint is they do not share
  a vertex apart from, maybe, the first and last vertices on the
  paths.}
%
In the fault tolerant
version of \scp we are given $r$ costs functions $c_1,\ldots,c_r$, and
we are looking for an $r$-robust placement that minimize the total
cost:
\[
\sum_{i=1}^r c_i(f_i) = \sum_{i = 1}^r \sum_j c_i(\alpha_j,f_i(\alpha_j))
~.
\]
We refer to this problem as $r$-robust \scp.
%
The motivation for using different costs functions is that it may be
the case that the first placement is the primal placement that may be
replaced by one of the other placements in case of a malfunction along
the physical path that is used by $f_1$.  Hence, the cost function
$c_2$ may take into account the probability of using the placement
$f_2$.

>>>>

Foerster, Parham and Schmid~\cite{FPS17} considered the
\textsc{Bidirectional Waypoint Routing} problem, where the input
consists of a graph $G = (V,E)$ with edge weights and capacities, a
source $s$, a destination $t$, and a subset of the vertices $W$.  A
feasible solution is a route from $s$ to $t$ that visits the vertices
in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
according to the given order.  The goal is to find a minimum weight
solution.
%
Foerster et al.~\cite{FPS17} showed that the unordered
problem has no PTAS, assuming P$\neq$NP and gave a
$1.53$-approximation algorithm.  They also presented polynomial time
algorithms for special cases.
%
As for the ordered variant, they showed that feasible routes can be
computed efficiently if $\abs{W} = O(1)$.  In addition, they showed
that the problem is NP-hard and gave a polynomial time algorithm for
cactus graphs with constant link capacities.
%
Amiri et al.~\cite{AFS18} considered the unordered case, and they
presneted a polynomial-time algorithm for graphs of bounded treewidth.
%
Amiri et al.~\cite{AFJPS18} studied the ordered case, and they
gave algorithms for special networks.
%
An overview of waypoint routing is given in \cite{AFJS18}.

@@

\item[Virtual specification:]
%
  The description of a request for a service chain consists of a
  physical source $s \in V$, a physical destination $t \in V$, and a
  directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
%
  Without loss of generality, we assume that $p(s) = p(t) = 0$.  
%
  The DAG $\calG$ has a source node $\sigma \in \calV$ and a
  destination $\tau \in \calV$. Each node $\alpha \in \calV$ represent
  a VNF that has a processing demand $p(\alpha)$.
%
  Without loss of generality, we assume that $p(\sigma) = p(\tau) =
  0$.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.

@@

Formally, given a physical network, a virtual specification, and a
parameter $r \in \naturals$, an \emph{$r$-robust} placement is a
collection of $r$ placements, $f_1,\ldots,f_r$, that correspond to $r$
internal vertex disjoint physical paths.%
\footnote{Two paths are internal vertex disjoint if they do not share
  a vertex apart from, maybe, the first and last vertices on the
  paths.}
%
In the fault tolerant
version of \scp we are given $r$ costs functions $c_1,\ldots,c_r$, and
we are looking for an $r$-robust placement that minimize the total
cost:
\[
\sum_{i=1}^r c_i(f_i) = \sum_{i = 1}^r \sum_j c_i(\alpha_j,f_i(\alpha_j))
~.
\]
We refer to this problem as $r$-robust \scp.
%
The motivation for using different costs functions is that it may be
the case that the first placement is the primal placement that may be
replaced by one of the other placements in case of a malfunction along
the physical path that is used by $f_1$.  Hence, the cost function
$c_2$ may take into account the probability of using the placement
$f_2$.
